What's in a Domain? Anaylsis of URL Features

### 2022-09-29 paper/paper.tex
reference add
Fleshing out experiments for paper

\begin{table}
  \caption{Attention Measurement Model - Aggregate Error}
  \label{tab:atm}
\begin{tabular}{|l|r|r|}
\toprule
Metric                  &Banner       &MREC       \\
\midrule
Aggregate MAE           &10.5 ms      &12.5 ms    \\
95\% Upper Bound        &19.0 ms      &20.6 ms    \\
95\% Lower Bound        &-22.8 ms     &-31.1 ms   \\
  \bottomrule
\end{tabular}
\end{table}

The signals collected along with the eye tracking data allow us to build and deploy an
attention measurment model that can predict the attention time paid to
specific ad units within a page. The attention model can
be applied to all digital inventory that accepts the javascript tag.

Our model evaluation process focuses on the accuracy of measuring mean
attention time for a specific ad format, over varying samples of inventory.
To generate the performance statistics we run bootstrap sampling of the test data
to look at the expected error when predicting the mean attention time over
impressions for a specific ad format. Each metric is calculated by taking 50 impression
samples 2000 times, and using the resulting distribution of mean error.
The mean attention time measurement performance is summarised in Table
\ref{tab:atm}.
We see that the aggregate mean absolute error (MAE) for both formats is very low
at $10.5 ms$ and $12.5 ms$ for banners and MRECs respectively. Furthermore, the
$95\%$ confidence intervals for these values is tightly constrained to be well under
$50 ms$ either side of the true value.
We apply this attention measurement model across large scale digitial inventory to
collect a data set of attention time paid to a range of advertisments over time.
We use these attention measured impressions to investigate the
impact of contextual categories of media on the attention paid to advertising.

@@

The data used in this study was collected from a collction of publications that 
present internet classification problems containing URLs as a key, or sole feature.
Malcious URL classification \cite{Mamun2016}.

4 Universities data http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-20/www/data/

\begin{table}
\caption{Datasets}
\label{tab:dataset}
\begin{tabular}{|l|r|r|}
\toprule
Metric          &Feb 18 - 24    &Feb 25 - March 03          \\
\midrule
Impressions     &16,895,661     &10,488,816     \\
URLS            &26,006         &27,855         \\
Domains         &2,263          &2,585          \\
Creatives       &683            &683            \\
Advertisers     &59             &59             \\
\bottomrule
\end{tabular}
\end{table}

>>>>

We design a feature extraction library for URLs that is sensitive to the various sections of URL
structure outlined above. We then apply this library to multiple machine learning tasks using only URLs
as the input variable. We experiment with multiple standard machine learning techniques and evaluate
the impact of the URL features using the SHAP package for feature importance.

\subsection{Features}

The features generated by the url2feature package are summaize in Table \ref{tab:features}

@@

The data used in this study was collected from a collction of publications that 
present internet classification problems containing URLs as a key, or sole feature.
The IS Malcious URL classification dataset contains both malware and phishing URLS 
that need to be discriminated against benign URLS\cite{Mamun2016}.
The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
range of university URLs categorised into multiple topic categories\cite{Craven1998}.
These 3 URL classification problems are summarised in Table \ref{tab:data}

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|}
\toprule
Dataset        &Records        &Classes  \\
\midrule
Malware        &               &2        \\
Phishing       &               &2        \\
WebKb 4Uni     &               &7        \\
\bottomrule
\end{tabular}
\end{table}
